%% 研究会原稿用の和文・英文テンプレート
%%   v1.0 [2005/06/14]

%% 1. 和文論文
\documentclass{ieej-tec}
%\documentclass[usejistfm]{ieej-tec}
%\usepackage{graphicx}
\usepackage{url}
\usepackage{amsmath}
\usepackage[dvipdfmx]{graphicx}
\usepackage[dvipdfmx]{color}
\usepackage[varg]{txfonts}
\usepackage{bm}
\usepackage[caption=false]{subfig}
  
\def\ClassFile{\texttt{ieej-tec.cls}}
\def\PS{{\scshape Post\-Script}}
\def\AmSLaTeX{\leavevmode\hbox{$\cal A\kern-.2em\lower.376ex
 \hbox{$\cal M$}\kern-.2em\cal S$-\LaTeX}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
 T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\def\labelenumi{\arabic{enumi})}

%\newenvironment{listnumlabel}
%\begin{list}{}{
%\usecounter{enumi}
%\def\makelabel#1{\refstepcounter{enumi}
%\bfseries\hbox to1.5zw{\hss\arabic{enumi}.}\hskip.5zw ##1\hss}
%\leftmargin=7zw\rightmargin=1zw\labelsep=1zw
%\labelwidth=6zw}}{\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	注意　勝手に変えたので…
\voffset=-3.0cm  %--> 上に 10mm 移動
\hoffset=-2.5cm  %--> 左に 10mm 移動
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\論文番号{MEC-19-022}
\jtitle{半導体歪ゲージを用いたハイダイナミックレンジ1軸力覚センサの開発}
\etitle{Development of high dynamic range uniaxial force/torque sensor using semiconductor strain gauge}
\authorlist{
 \authorentry{田村 龍也*}{Ryuya Tamura}{saitamaone}
 \authorentry{境野 翔}{Sho Sakaino}{tsukuba}
 \authorentry{辻 俊明}{Toshiaki Tsuji}{saitamatwo}
}
\affiliate[saitamaone]
{埼玉大学}
{Saitama University}
\affiliate[tsukuba]
{筑波大学, JSTさきがけ}
{University of Tsukuba, JST/presto}
\affiliate[saitamatwo]
{埼玉大学}
{Saitama University}

%\breakaffiliate{1}
%\breakJauthorline{3}
%\breakEauthorline{3}

\begin{document}
\begin{abstract}

A force/torqe is often requird to delect small  forse while its maximum load 
is also often large. In other words, the dynamic range of force sensors 
should be higher.  In order to extend the dynamic range of 
the force/torque sensor, a high dynamic range force sensor that uses 
both semiconductor strain gauges and general strain gauges was developed. 
Experimental results show that the dynamic range can be extended without 
complicating the structure of the strain body.

\end{abstract}
\begin{jkeyword}
  力計測，力制御，ハプティクス
\end{jkeyword}
\begin{ekeyword}
  Force sensing，Force control，Haptics Tactile sensing
\end{ekeyword}
\maketitle

\input{./src/introduction}

\input{./src/principle}

\input{./src/design}

\input{./src/Experiment}

\input{./src/Summary} 

\input{./src/Acknowledgements}


\begin{thebibliography}{10}
%\bibliographystyle{plain}    %参考文献出力スタイル(欧文)
%\bibliographystyle{junsrt}    %参考文献出力スタイル(和文)
   %1
   \bibitem{blumenkranz2018force}
   S. J. Blumenkranz, G. M. Prisco, S. P. DiMaio, W. D. Gregory II, H. Dostmohamed, C. J. Hasser, and G. S. Guthart, ``Force and torque sensing in a surgical robot setup arm,\,'' Google Patents, US Patent 9,895,813, 2018.
   %2
   \bibitem{Berkman2003}
   P. J. Berkelman, L. L. Whitcomb, R. H. Taylor, and P. Jensen, ``A miniature microsurgical instrument tip force sensor for enhanced force feedback during robot-assisted manipulation," \emph{IEEE Trans. on Robotics and Automation}, 2003, Vol.~19, No.~5, pp.~917--921.
   %3
   %\bibitem{Kaasaki2002}
   %H. Kawasaki, T. Komatsu, and K. Uchiyama, ``Dexterous anthropomorphic robot hand with distributed tactile sensor: Gifu hand II,"\emph{IEEE/ASME Trans. on Mechatronics}, 2002, Vol.~7, No.~3, pp.~296--303.
   %4
   \bibitem{Bouyarmane2019}
   K. Bouyarmane, K. Chappellet, J. Vaillant, and A. Kheddar, ``Quadratic programming for multirobot and task-space force control." \emph{IEEE Trans. on Robotics}, 2019, Vol.~35, No.~1, pp.~64--77. 
   %5
   \bibitem{Jacq2019}
   C. Jacq, B. L?thi, T. Maeder, O. Lambercy, R. Gassert, and P. Ryser, ``Thick-film multi-DOF force/torque sensor for wrist rehabilitation," \emph{Sensors and Actuators A: Physical}, 2010, Vol.~162, No.~2, pp.~361--366.
   %6
   \bibitem{yokoo2012}
   T. Yokoo, M. Yamada, S. Sakaino, S. Abe, and T. Tsuji, ``Development of a physical therapy robot for rehabilitation databases," in \emph{Proc. IEEE Int. Workshop on Advanced Motion Control (AMC)}, 2012, pp.~1--6.

\bibitem{Jiang2015}
J. Jiang, W. Chen, J. Liu, W. Chen, and J. Zhang.
\newblock {Design of a Dual-Range Force Sensor for Achieving High Sensitivity,
  Broad Bandwidth, and Large Measurement Range}.
\newblock {\em IEEE Sens. J.}, Vol.~15, No.~2, pp. 1114--1123, 2015.

\bibitem{jiang2013}
J. Jiang, W. Chen, J. Liu, and W. Chen.
\newblock {A cost effective multi-axis force sensor for large scale measurement
  : design , modeling , and simulation}.
\newblock pp. 188--193, 2013.

\bibitem{murozaki2014miniaturized}
Y. Murozaki, K. Nogawa, and F. Arai.
\newblock {Miniaturized load sensor using quartz crystal resonator constructed
  through microfabrication and bonding}.
\newblock {\em Robomech J.}, Vol.~1, No.~1, p.~3, 2014.

\bibitem{okumura2018high}
D. Okumura, S. Sakaino, and T. Tsuji.
\newblock {High Dynamic Range Sensing by a Multistage Six-Axis Force Sensor
  with Stopper Mechanism}.
\newblock In {\em Proc. IEEE Int. Conf. Robot. Autom.}, pp. 1--6. IEEE, 2018.

\bibitem{Okumura}
辻俊明, 奥村大輔, 境野翔.
\newblock 多段型ハイダイナミックレンジ6軸力覚センサの小型化.
\newblock  日本ロボット学会学術講演会, 2018.

\bibitem{Ryuya}
R. Tamura, S Sakaino, and T. Tsuji.
\newblock {Development of compact high dynamic range six-axis force sensor 
with cross-arch structure}.
\newblock In {\em Proc. Annu. Conf. IEEE Ind. Electron. Soc}

\bibitem{nishiwaki2002six}
K. Nishiwaki, Y. Murakami, S. Kagami, Y. Kuniyoshi, M. Inaba, and H. Inoue.
\newblock {A six-axis force sensor with parallel support mechanism to measure
  the ground reaction force of humanoid robot}.
\newblock In {\em Proc. IEEE Int. Conf. Robot. Autom.}, Vol.~3, pp. 2277--2282,
  2002.

\bibitem{Liang2010}
 Q. Liang, D. Zhang, Q. Song, Y. Ge, H. Cao, and Yu~Ge.
 \newblock {Design and fabrication of a six-dimensional wrist force / torque
   sensor based on E-type membranes compared to cross beams}.
 \newblock {\em Measurement}, Vol.~43, pp. 1702--1719, 2010.

\bibitem{Beyeler2009}
F. Beyeler, S. Muntwyler, and B. J. Nelson.
\newblock {A six-axis MEMS force-torque sensor with micro-Newton and
  nano-Newtonmeter resolution}.
\newblock {\em J. Microelectromechanical Syst.}, Vol.~18, No.~2, pp. 433--441,
  2009.

\bibitem{Kim2013a}
J. C. Kim, K. S. Kim, and S. Kim.
\newblock {Note: A compact three-axis optical force/torque sensor using
  photo-interrupters}.
\newblock {\em Rev. Sci. Instrum.}, Vol.~84, No.~12, pp. 77--80, 2013.

\bibitem{su20093}
H. Su and G. S. Fischer.
\newblock {A 3-axis optical force/torque sensor for prostate needle placement
  in magnetic resonance imaging environments}.
\newblock In {\em Proc. IEEE Int. Conf. Technol. Pract. Robot Appl.}, pp. 5--9.
  IEEE, 2009.

\bibitem{polygerinos2010novel}
P. Polygerinos, P. Puangmali, T. Schaeffter, R. Razavi,
  L. D. Seneviratne, and K. Althoefer.
\newblock {Novel miniature MRI-compatible fiber-optic force sensor for cardiac
  catheterization procedures}.
\newblock In {\em Proc. IEEE Int. Conf. Robot. Autom.}, pp. 2598--2603. IEEE,
  2010.

%\bibitem{1991}
%緒方浩二郎, 柏木邦雄, 小野耕三.
%\newblock 力覚センサ, 1991.

%\bibitem{hanyu2010simplified}
%Ryosuke Hanyu, Toshiaki Tsuji, and Shigeru Abe.
%\newblock {A simplified whole-body haptic sensing system with multiple
%  supporting points}.
%\newblock In {\em Proc. IEEE Int. Work. Adv. Motion Control}, pp. 691--696.
 % IEEE, 2010.

%\bibitem{向井優2018}
%向井優, 野田善之.
%\newblock 六軸力覚センサの原理と構造.
%\newblock 精密工学会誌, Vol.~84, No.~4, pp. 303--306, 2018.


%\bibliography{C:/Users/Kohei/Documents/library}           %data.bibから拡張子を外した名前

%\appendix
  %\input{./src/Refernces}
\end{thebibliography}

%\input{./src/ExperimentFig}

\end{document}