\documentclass[usejistfm]{ieej}
\usepackage{url}
\usepackage{amsmath}
\usepackage[dvipdfmx]{graphicx}
\usepackage[dvipdfmx]{color}
\usepackage[varg]{txfonts}
\usepackage{bm}
\usepackage[caption=false]{subfig}

%\usepackage[top=0.5in]{geometry}
%\usepackage{fullpage}
%\usepackage{auto-pst-pdf}
%\usepackage{epstopdf}
%\usepackage{float}
\usepackage{subfloat}
%\usepackage{caption}
%\usepackage{axodraw4j}
%\usepackage{pstricks}


\jtitle{半導体歪ゲージを用いたハイダイナミックレンジ1軸力覚センサの開発}
%\etitle{Development of a compact high dynamic range 6-axis force/torque sensor}
\authorlist{
 \authorentry{19MM227\ \ \ 田村 龍也}{Ryuya Tamura}{s}{TRL}
 }
%\affiliate[] {埼玉大学工学部電気電子システム工学科\\
 %〒338--8570\ 埼玉県さいたま市下大久保255}
  %{Saitama\ University \\
  %255, Shimo-ohkubo, Sakura-ku\ Saitama\ 338--8570}
\begin{document}
\begin{abstract}

%\input{./src/Abstract}

\end{abstract}
%\begin{jkeyword}
 %力覚センサ，ダイナミックレンジ, 小型化, 分解能
%\end{jkeyword}
%\begin{ekeyword}
 %Force/Torque sensor, Dynamic range, Miniaturization, Resolution
%\end{ekeyword}
\maketitle


\input{./src/introduction}

\input{./src/principle}

\input{./src/design}

\input{./src/Experiment}

\input{./src/Summary} 

\input{./src/Acknowledgements}


\begin{thebibliography}{10}
%\bibliographystyle{plain}    %参考文献出力スタイル(欧文)
%\bibliographystyle{junsrt}    %参考文献出力スタイル(和文)
\bibitem{denso}
力センサ有コンプライアンス機能.
\url{https://www.denso-wave.com/ja/robot/product/function/Acontact.html}
[Online; accessed 2019-02-14] 

\bibitem{asimo}
{Honda|ASIMO}.
\url{https://www.honda.co.jp/ASIMO/}.
[Online; accessed 2019-02-14] 

\bibitem{ROBEAR}
{介護支援ロボット研究用プラットフォームROBEAR}.
\url{http://rtc.nagoya.riken.jp/ROBEAR/}.
[Online; accessed 2019-02-14] 

\bibitem{yoshikawa1989six}
Tsuneo Yoshikawa and Taizou Miyazaki.
\newblock {A six-axis force sensor with three-dimensional cross-shape
  structure}.
\newblock In {\em Proc. IEEE Int. Conf. Robot. Autom.}, pp. 249--255. IEEE,
  1989.

%\bibitem{nishiwaki2002six}
%Koichi Nishiwaki, Yoshifumi Murakami, Satoshi Kagami, Yasuo Kuniyoshi, Masayuki
 % Inaba, and Hirochika Inoue.
%\newblock {A six-axis force sensor with parallel support mechanism to measure
%  the ground reaction force of humanoid robot}.
%\newblock In {\em Proc. IEEE Int. Conf. Robot. Autom.}, Vol.~3, pp. 2277--2282,
%  2002.

%\bibitem{Liang2010}
% Qiaokang Liang, Dan Zhang, Quanjun Song, Yunjian Ge, Huibin Cao, and Yu~Ge.
% \newblock {Design and fabrication of a six-dimensional wrist force / torque
%   sensor based on E-type membranes compared to cross beams}.
% \newblock {\em Measurement}, Vol.~43, pp. 1702--1719, 2010.

\bibitem{Beyeler2009}
Felix Beyeler, Simon Muntwyler, and Bradley~J. Nelson.
\newblock {A six-axis MEMS force-torque sensor with micro-Newton and
  nano-Newtonmeter resolution}.
\newblock {\em J. Microelectromechanical Syst.}, Vol.~18, No.~2, pp. 433--441,
  2009.

\bibitem{Kim2013a}
Ji~Chul Kim, Kyung~Soo Kim, and Soohyun Kim.
\newblock {Note: A compact three-axis optical force/torque sensor using
  photo-interrupters}.
\newblock {\em Rev. Sci. Instrum.}, Vol.~84, No.~12, pp. 77--80, 2013.

%\bibitem{su20093}
%Hao Su and Gregory~S Fischer.
%\newblock {A 3-axis optical force/torque sensor for prostate needle placement
%  in magnetic resonance imaging environments}.
%\newblock In {\em Proc. IEEE Int. Conf. Technol. Pract. Robot Appl.}, pp. 5--9.
%  IEEE, 2009.

%\bibitem{polygerinos2010novel}
%Panagiotis Polygerinos, Pinyo Puangmali, Tobias Schaeffter, Reza Razavi,
%  Lakmal~D Seneviratne, and Kaspar Althoefer.
%\newblock {Novel miniature MRI-compatible fiber-optic force sensor for cardiac
%  catheterization procedures}.
%\newblock In {\em Proc. IEEE Int. Conf. Robot. Autom.}, pp. 2598--2603. IEEE,
%  2010.

\bibitem{Jiang2015}
Jun Jiang, Weihai Chen, Jingmeng Liu, Wenjie Chen, and Jianbin Zhang.
\newblock {Design of a Dual-Range Force Sensor for Achieving High Sensitivity,
  Broad Bandwidth, and Large Measurement Range}.
\newblock {\em IEEE Sens. J.}, Vol.~15, No.~2, pp. 1114--1123, 2015.

\bibitem{jiang2013}
Jun Jiang, Weihai Chen, Jingmeng Liu, and Wenjie Chen.
\newblock {A cost effective multi-axis force sensor for large scale measurement
  : design , modeling , and simulation}.
\newblock pp. 188--193, 2013.

\bibitem{murozaki2014miniaturized}
Yuichi Murozaki, Kousuke Nogawa, and Fumihito Arai.
\newblock {Miniaturized load sensor using quartz crystal resonator constructed
  through microfabrication and bonding}.
\newblock {\em Robomech J.}, Vol.~1, No.~1, p.~3, 2014.

\bibitem{okumura2018high}
Daisuke Okumura, Sho Sakaino, and Toshiaki Tsuji.
\newblock {High Dynamic Range Sensing by a Multistage Six-Axis Force Sensor
  with Stopper Mechanism}.
\newblock In {\em Proc. IEEE Int. Conf. Robot. Autom.}, pp. 1--6. IEEE, 2018.

\bibitem{Okumura}
辻俊明, 奥村大輔, 境野翔.
\newblock 多段型ハイダイナミックレンジ6軸力覚センサの小型化.
\newblock  日本ロボット学会学術講演会, 2018.

\bibitem{1991}
緒方浩二郎, 柏木邦雄, 小野耕三.
\newblock 力覚センサ, 1991.

\bibitem{hanyu2010simplified}
Ryosuke Hanyu, Toshiaki Tsuji, and Shigeru Abe.
\newblock {A simplified whole-body haptic sensing system with multiple
  supporting points}.
\newblock In {\em Proc. IEEE Int. Work. Adv. Motion Control}, pp. 691--696.
  IEEE, 2010.

\bibitem{向井優2018}
向井優, 野田善之.
\newblock 六軸力覚センサの原理と構造.
\newblock 精密工学会誌, Vol.~84, No.~4, pp. 303--306, 2018.


%\bibliography{C:/Users/Kohei/Documents/library}           %data.bibから拡張子を外した名前

%\appendix
  %\input{./src/Refernces}
\end{thebibliography}

%\input{./src/ExperimentFig}

\end{document}